Storing messages with multipartite neural cliques

### 2014-07-18 Articles/article.tex
...

	We first describe how messages can be stored in a binary clustered network of multipartite cliques. Secondly we detail how messages can be retrieved after being stored in such a network.

@@

		We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve. We set $\tilde{x}^0 = \tilde{x}$.

@@

@@

	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(l, l')$ to be present in the network (i.e. $W_{ll'} = 1$). We then express the theoretical error rate after one iteration of the retrieving rule in function of the density. All this computations are done assuming connections between units are independent, which is false but is a convenient approximation that gives results very close from empirical results.

@@

	Erasures of a symbol in a message corresponds to an erased cluster in the network. An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.

>>>>

	We first describe how messages can be stored in a binary clustered network of multipartite cliques. Secondly we detail how messages can be retrieved after being stored in such a network, thereby showing how such a network can be used as an associative memory.

@@

		We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve. We set $\tilde{x}^0 = \tilde{x}$. The network is in state $\tilde{x}$ at the beginning of the retrieving. The message will be successfully retrieved if at the end of the algorithm, the network is in state $x$.

@@

	One can see a partial version of a message $x$ as the result of erasures of symbols of $x$. Some symbols of $x$ are replaced by the blank character $\intercal$.	Erasures of a symbol in a message corresponds to an "erased" cluster in the network. An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.

@@

	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(l, l')$ to be present in the network (i.e. $W_{ll'} = 1$). We then express the theoretical error rate after one iteration of the retrieving rule in function of the density. All this computations (on error rates) are done assuming connections between units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.

@@
